%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Nicholas Lange
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Nicholas Lange}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    2015 Frederick Norris Pl.   \hfill mobile: +1 (250) 893-3550          \vspace{0mm}\\\vspace{0mm}%
    Victoria, BC                \hfill e-mail: nick.t.lange@gmail.com     \vspace{0mm}\\\vspace{0mm}%
    V8P 2B1, Canada             \hfill   \vspace{0mm}\\\vspace{-4.5mm}%



    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Victoria}, Victoria, BC, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Master of Science} \hfill \textbf{ September 2013 -- December 2015}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Theoretical Physics
        \item Worked on adding a new scalar/vector particle to standard model to solve proton radius puzzle
        \item GPA: 8.83 (9 point scale)
    \end{list2}\vspace{2mm}

    \textbf{University of Victoria}, Victoria, BC, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor of Science} \hfill \textbf{ September 2008 -- November 2012}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Honours Physics \& Computer Science with Distinction
        \item GPA: 8.15 (9 point scale)
    \end{list2}\vspace{2mm}

    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Skills} 

    \textbf{Languages}: C++, Python, Java, C, Mathematica, Matlab, Linux shell scripting, XML, \LaTeXe, SQL, IDL, IRAF, ARM Assembly.\vspace{1mm}\\
    \textbf{Tools}: Vim, Microsoft Visual Studio C++, Eclipse, SVN, Git, GDB, Bugzilla.\vspace{1mm}\\
    \textbf{Operating systems}: Familiar with Windows and UNIX environments, experience writing code for the Android platform.\vspace{1mm}\\
    \textbf{Server management}: Experience creating and managing UNIX and Windows servers, configuring virtual machine hosts/clients with VSphere, various servers in software (MySQL, Apache, Tomcat, etc.), Amazon EC2.\vspace{1mm}\\
    \textbf{Physics}: Research interests in particle physics, experience with quantum field theory, cosmology, and statistical mechanics, among standard undergraduate physics topics.\vspace{1mm}\\
    \textbf{Math}: Strong skills in linear algebra, Fourier filtering methods, fitting, statistical analysis, error analysis.\vspace{1mm}\\
    \textbf{Laboratory techniques}: Experience using a wide variety of instrumentation, well documented lab reports, circuit design and construction.\vspace{1mm}\\
    \textbf{General}: Strong problem solving skills, diagnosis of hardware \& software issues, well organized and motivated, work well both independently and in groups.\vspace{1mm}\\

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \vspace{-5mm}
    \section{\mysidestyle Professional\\Experience}

    \textbf{Safe Software}, Surrey, BC, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Development Intern} \hfill \textbf{May  2012 -- August 2012; April 2013 -- August 2013}\\
    {\small
        Worked implementing features and bugfixes in FME (Feature Manipulation Engine) with the XML team.
    Added ability for FME to store data in Amazon S3, Amazon DynamoDB, and query support for Amazon Redshift and Google BigQuery in Java.
    Implemented an HTTP client wrapper over cURL, SOAP formatters, and other XML/HTTP related objects in C++.
    Team consisted of only three members, so lots of self-direction was required but working closely with the group was often required.}

    \textbf{Gemini Observatory}, Hilo, Hawaii, United States of America \vspace{2mm}\\\vspace{1mm}%
    \textsl{Instrumentation Intern} \hfill \textbf{May  2010 -- August 2010}\\
    {\small
    Assisted with Gemini's instrument NIRI (Near Infrared Imager) non-linearity problem.
    Created sequences to run on telescope to determine cause of problem.
    Required writing many Python scripts to reduce, analyze, fit using Matplotlib and NumPy, and correct data. }

    \newpage

    \textbf{National Research Council of Canada - Herzberg Institute of Astrophysics},\\ Victoria, BC, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Research Intern} \hfill \textbf{May  2009 -- August 2009}\\
    {\small
    Reduced and analyzed lightcurves to determine which stars may be variable and spectra to investigate Wolf-Rayet stars.
    The IDL language was used to analyze the lightcurves and IRAF was used to reduce the spectra.
    Operated the 1.8m Plaskett telescope for 3 weeks to obtain spectra and imaging data.
    A publication using the data taken has been published by the Institute for Computational Astrophysics (SMUICA-12-133) and can be found in the Monthly Notices of the Royal Astronomical Society, Volume 426, Issue 3, pp. 1720-1730.}
    

    \textbf{Self Employed}, Mayne Island, BC, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Freelance Computer Technician} \hfill \textbf{June 2004 -- August 2008}\\
    {\small
    Offered computer repair services for both hardware and software problems.
    Marketed business through the local newspaper.
    Entirely self directed work on site.
    Required rapid diagnosis and problem solving.}

    \textbf{Cottage Computers}, Mayne Island, BC, Canada \vspace{2mm}\\\vspace{1mm}%
    \textsl{Technical Support \& Sales Person} \hfill \textbf{June 2003 -- August 2006}\\
    {\small
    Troubleshot software and hardware issues for customers. Configured and built new systems for users to purchase.
    Ran store in a self directed manner as no supervisor was present on most days.
    Setup network for the internet caf\'{e} for customers to use.}
    \vspace{2mm}

    
    %__________________________________________________________________________________________________________________
    % Honours and Awards
    \section{\mysidestyle Honours and\\Awards} 

    Eric Forster Graduate Scholarship in Physics \hfill 2015\vspace{1mm}\\%
    Outstanding Graduate Entrance Award \hfill 2013\vspace{1mm}\\%
    University of Victoria Fellowship \hfill 2013\vspace{1mm}\\%
    Graduation with Distinction (Top 20\% of graduating class) \hfill 2012\vspace{1mm}\\%
    Johannes G. Nordal Scholarship in Engineering \hfill 2011\vspace{1mm}\\%
    President's Scholarship \hfill 2009, 2010, 2011\vspace{1mm}\\%
    University of Victoria Entrance Scholarship \hfill 2008\vspace{1mm}\\%
    Mayne Island Lion's Club Scholarship \hfill 2008-2012\vspace{1mm}\\%
%   100\% Club for Calculus 12 \hfill 2008\vspace{1mm}\\%
%   Principal's List \hfill  2008\vspace{1mm}\\%
%   Honour Roll \hfill 2008\vspace{1mm}\\%
%   TRU Chemistry Contest Chemistry 11 \& 12: Top in School \hfill 2008\vspace{1mm}\\%
%   Excellence in Animation \hfill 2008

    \section{\mysidestyle Activities and Interests}
    \begin{list2}
    \item I enjoy playing classical and ragtime music on the piano, and I'm slowly getting into classic rock.
    \item Machine learning has become an interest of mine, and I participate in the UVic Machine Learning Club, where we attempt to solve challenges posted online.
    \item Riding my bike is quite relaxing and is a rewarding way to start a day off. When possible, I try to bike.
    \item At my house, I host a variety of servers which I like to maintain for friends and myself to use.
            This includes a fully functioning 28TB fileserver, a helpdesk, a voice-chat server (Mumble), some game servers, a VPN, a VSphere host, and more.
            As often as possible I run them on Linux, usually Fedora, and feel very comfortable working at the command line. 
    \item Rubik's cubes can waste a day for me. So far I've undertaken some of the larger cubes (5x5x5) and some other oddly shaped ones,
            like the hexagon shaped puzzle.
    \item Programming is something that interests me because it gives me the ability to build complex systems using a language that feels natural.
            I've written some primitive games (Pong clones, Chess, etc.) and a few utilities I've found useful.
            A few of these are hosted on my personal Github account (github.com/drglove).
            In particular, my Android program to check grades at UVic has been helpful during the exam season for myself and classmates and has been published on the Play Store.
    \item In the time off inbetween my undergraduate and graduate studies, I began my Private Pilot's License at the Victoria Flying Club. In the future I would like to return to complete my training.
    \end{list2}
    \vspace{2mm}

    %__________________________________________________________________________________________________________________
    % References
    \section{\mysidestyle References} 

    %\begin{tabular}{@{}p{6cm}p{6cm}}
    %\textbf{Dr. Andrew Stephens}             &  \textbf{Dr. Andr\'{e}-Nicolas Chen\'{e}}          \\
    %Assistant Scientist                      &  Assistant Scientist                               \\
    %Gemini North Observatory                 &  Gemini North Observatory                          \\
    %Hilo, HI, US                             &  Hilo, HI, US                                      \\
    %phone: \textsl{+1 (808) 974-2611}        &                                                    \\
    %e-mail: \textsl{astephens@gemini.edu}    &  e-mail: \textsl{andrenicolas.chene@gmail.com}     \\
    %\end{tabular}

    %\begin{tabular}{@{}p{6cm}p{6cm}}
    %\textbf{Juan Chu Chow}                 &  \textbf{Dr. Martial Agueh}                \\
    %Senior Application Developer           &  Associate Professor                      \\
    %Safe Software                          &  University of Victoria                   \\
    %Surrey, BC, Canada                     &  Department of Math and Statistics        \\
    %                                       &  Victoria, BC, Canada                     \\
    %phone: \textsl{+1 (604) 501-9985}      &  phone: \textsl{+1 (250) 721-7466}        \\
    %e-mail: \textsl{juan.chuchow@safe.com} &  e-mail: \textsl{agueh@math.uvic.ca}      \\
    %\end{tabular}
    Available upon request.



%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

